---
title: "Transmondyn"
author: "Rey; Cura"
date: "22/10/2014"
output: ioslides_presentation
runtime: shiny
---

## Shiny Presentation

This R Markdown presentation is made interactive using Shiny. The viewers of the presentation can change the assumptions underlying what's presented and see the results immediately. 

To learn more, see [Interactive Documents](http://rmarkdown.rstudio.com/authoring_shiny.html).

## Slide with Interactive Plot (1)
```{r, echo=FALSE}
library(RNetLogo)
library(ggplot2)

currentUser <- as.list(Sys.info())$user
if (currentUser  == "robin"){
  nlDir <- "/home/robin/Downloads/netlogo-5.0.5/"
} else {
  nlDir <- "/home/srey/Binaire/netlogo-5.0.4/"
}

setwd(nlDir)
 
nl.path <- getwd()
NLStart(nl.path, gui = FALSE) # start NetLogo "headless"
 
model.path <- file.path("models", "Sample Models", "Earth Science","Fire.nlogo")
NLLoadModel(file.path(nl.path, model.path))

NLCommand("set density 60")
NLCommand("setup")
burned <- NLDoReportWhile("any? turtles", "go",
                c("ticks", "(burned-trees / initial-trees) * 100"),
                as.data.frame = TRUE, df.col.names = c("tick", "percent.burned"))
# Plot with ggplot2
p <- ggplot(burned,aes(x=tick,y=percent.burned))
p + geom_line() + ggtitle("Non-linear forest fire progression with density = 60")
```

## Slide with Interactive Plot

```{r, echo=FALSE}
inputPanel(
  selectInput("n_breaks", label = "Number of bins:",
              choices = c(10, 20, 35, 50), selected = 20),
  
  sliderInput("bw_adjust", label = "Bandwidth adjustment:",
              min = 0.2, max = 2, value = 1, step = 0.2)
)

renderPlot({
  hist(faithful$eruptions, probability = TRUE, breaks = as.numeric(input$n_breaks),
       xlab = "Duration (minutes)", main = "Geyser eruption duration")
  
  dens <- density(faithful$eruptions, adjust = input$bw_adjust)
  lines(dens, col = "blue")
})
```

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Code and Output

```{r}
summary(cars)
```


